Target for the data

### 2023-02-23 build/code/exploration/data_structure.Rmd
housekeeping build folder

## What would I run the regressions on?

The regression would look something like this:

```{r cars}
reg1 <- lm(pop ~ city_fe + year_fe + treat*post + controls)
```

Ideally, I want a city-year level dataset with an entry for every year, based on the ruler dataset, not the territories dataset. For any given year, I want to know immediately not only the city's ruling lineage, but also the ruler. And then, for these city-year observations, I can add my outcome variables.

@@

How do I do that? It seems to me that this kind of works like a relational database.
Each city-year observation must have non-missing lineage. Each lineage-year observation must have a non-missing ruler. That's how I could get there.

@@

But first let me check whether this is already in `cities_families.dta`.

```{r cities data}
cities <- read_dta('build/input/cities_families_1300_1918.dta')
summary(cities)
view(cities)
```

Okay, perfect. That file already contains the lineages for all cities for all years. At first glance it seems to be exactly what I would have had to do with the territories data - expand it so there's an observation for each year, based on the exact years in the commentary fields. That would have been a huge pain.

### Ruler for all lineage-year observations

The file `family_rulers_imputed.dta` is a list of ruler-level observations. These rulers happen to be in chronological order, but they're not lineage-year observations. Yet. How do I get them there?

```{text pseudo-code}
lineages <- expand(terr_id x year)
lineages <- mutate(ruler_id = case_when(
  year %in% start_reign:end_reign ~ ruler_id
))
```

Something like that may get the job done, but it seems computationally intensive and unelegant. Mathematically, what am I trying to do? I'm not trying to map lineage-year observations to rulers. I'm

Maybe do a function, or a dictionary. You input a terr_id and a year. It filters the rulers data down to the terr_id. Then it drops all rulers with reigns ending before or starting after that year. it returns the ruler of that lineage of that year.

Then `map` year-lineage entries to rulers with that function.

>>>>

I want a city-year panel of
- construction activity
- ruling lineage (terr_id)
- ruling lineage's extinction in that year
- cities held by ruling lineage in that year
- controls (capital status, conflict)

@@

It seems to me that this kind of works like a relational database. Each city-year observation has non-missing ruling lineage. Each lineage-year observation has non-missing extinction dummy and size.

@@

This is already in `cities_families.dta`. The lineage is given for every city-year observation.

```{r cities data}
cities <- read_dta('build/input/cities_families_1300_1918.dta')
summary(cities)
view(cities)
```
### Extinction for all lineage-year observations

The file `family_rulers_imputed.dta` is a list of person-level observations. I turn this into a lineage-year panel of rulers in the same way I did for work: filter for non-missing terr_id. 
(This relies on what Matthias told me to do in summer being correct. I should verify my implicit assumptions about the dataset - that non-rulers in `family_rulers_imputed.dta` have missing terr_id, and that the ruler list is therefore a lineage-year panel of rulers.)

Then I can obtain the extinction year of each lineage by filtering for the last ruler in each lineage (max start_reign). This ruler's death_year is the extinction year of the lineage (or where our data ends. In a future iteration of this, I could use the `territories.csv` data to cross-validate.)

### Size for all lineage-year observations

Use number of cities. You can recycle code you wrote in the territories project.

## Merging / joining the relational data

Find out how this works once you have constructed everything.
